---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(ggplot2)
```


```{r}
data <- read.csv('KNN_Export.csv', header = T)
data
```


```{r}
data_scratch <- data[which(data$Identifier == 'KNN FROM SCRATCH'), ]
data_sklearn <- data[which(data$Identifier == 'KNN SKLEARN'), ]

data_scratch
```


```{r}
ggplot(NULL) +
  geom_line(data = data_scratch, aes(x = Number.of.Neighbors
, y = Precision, color = "A"), show.legend = TRUE) +
  geom_line(data = data_sklearn, aes(x = Number.of.Neighbors
, y = Precision, color = "B"), show.legend = TRUE) +
  scale_y_continuous(limits = c(0.8, 1)) +
  scale_color_manual(values = c("A" = "red", "B" = "blue"), 
                       labels = c("KNN from scratch", "KNN sklearn"),
                       name = "Algorithms") +
  labs(x = "Hyper-Parameter k", title = "Precision vs Hyper-Parameter k")
```


```{r}
ggplot(NULL) +
  geom_line(data = data_scratch, aes(x = Number.of.Neighbors
, y = F1.Score, color = "A"), show.legend = TRUE) +
  geom_line(data = data_sklearn, aes(x = Number.of.Neighbors
, y = F1.Score, color = "B"), show.legend = TRUE) +
  scale_y_continuous(limits = c(0.6, 1)) +
  scale_color_manual(values = c("A" = "red", "B" = "blue"), 
                       labels = c("KNN from scratch", "KNN sklearn"),
                       name = "Algorithms") +
  labs(x = "Hyper-Parameter k", title = "F1.Score vs Hyper-Parameter k")
```


```{r}
ggplot(NULL) +
  geom_line(data = data_scratch, aes(x = Number.of.Neighbors
, y = Accuracy, color = "A"), show.legend = TRUE) +
  geom_line(data = data_sklearn, aes(x = Number.of.Neighbors
, y = Accuracy, color = "B"), show.legend = TRUE) +
  scale_y_continuous(limits = c(80, 100)) +
  scale_color_manual(values = c("A" = "red", "B" = "blue"), 
                       labels = c("KNN from scratch", "KNN sklearn"),
                       name = "Algorithms") +
  labs(x = "Hyper-Parameter k", title = "Accuracy vs Hyper-Parameter k")
```
```{r}
ggplot(NULL) +
  geom_line(data = data_scratch, aes(x = Number.of.Neighbors
, y = Recall, color = "A"), show.legend = TRUE) +
  geom_line(data = data_sklearn, aes(x = Number.of.Neighbors
, y = Recall, color = "B"), show.legend = TRUE) +
  scale_y_continuous(limits = c(0.6,1)) +
  scale_color_manual(values = c("A" = "red", "B" = "blue"), 
                       labels = c("KNN from scratch", "KNN sklearn"),
                       name = "Algorithms") +
  labs(x = "Hyper-Parameter k", title = "Recall vs Hyper-Parameter k")
```
```{r}
ggplot(NULL) +
  geom_line(data = data_scratch, aes(x = Number.of.Neighbors
, y = Sensitivity, color = "A"), show.legend = TRUE) +
  geom_line(data = data_sklearn, aes(x = Number.of.Neighbors
, y = Sensitivity, color = "B"), show.legend = TRUE) +
  scale_y_continuous(limits = c(0.6,1)) +
  scale_color_manual(values = c("A" = "red", "B" = "blue"), 
                       labels = c("KNN from scratch", "KNN sklearn"),
                       name = "Algorithms") +
  labs(x = "Hyper-Parameter k", title = "Sensitivity vs Hyper-Parameter k")
```
```{r}
ggplot(NULL) +
  geom_line(data = data_scratch, aes(x = Number.of.Neighbors
, y = Specificity, color = "A"), show.legend = TRUE) +
  geom_line(data = data_sklearn, aes(x = Number.of.Neighbors
, y = Specificity, color = "B"), show.legend = TRUE) +
  scale_y_continuous(limits = c(0,0.1)) +
  scale_color_manual(values = c("A" = "red", "B" = "blue"), 
                       labels = c("KNN from scratch", "KNN sklearn"),
                       name = "Algorithms") +
  labs(x = "Hyper-Parameter k", title = "Specificity vs Hyper-Parameter k")
```


```{r}
ggplot(data_scratch) +
  geom_histogram(aes(x = Precision), colour="black", fill="white") +
  geom_density(aes(x = Precision), alpha=.2, fill="#FF6666") 

ggplot(data_sklearn) +
  geom_histogram(aes(x = Precision), colour="black", fill="white") +
  geom_density(aes(x = Precision), alpha=.2, fill="#FF6666")
```

```{r}
ggplot(NULL) +
  geom_line(data = data_scratch, aes(x = Number.of.Neighbors
, y = Processing.Time, color = "A"), show.legend = TRUE) +
  geom_line(data = data_sklearn, aes(x = Number.of.Neighbors
, y = Processing.Time, color = "B"), show.legend = TRUE) +
  scale_y_continuous(limits = c(.001, 2)) +
  scale_color_manual(values = c("A" = "red", "B" = "blue"), 
                       labels = c("KNN from scratch", "KNN sklearn"),
                       name = "Algorithms") +
  labs(x = "Hyper-Parameter k", title = "Processing Time vs Hyper-Parameter k")
```
Variance Test for Accuracy Metric
```{r}
var.test(data_scratch$Accuracy, data_sklearn$Accuracy, alternative = "two.sided")
```

```{r}
c(qf(0.025, 49, 49), qf(0.975, 49, 49))
```
Determining nu which would be useful to determine the critical region for our hypothesis

```{r}
a <- var(data_scratch$Accuracy)
b <- var(data_sklearn$Accuracy)

nu <- (((a/50) + (b/50)) ^ 2) / (((a/50)^2)/49) + (((b/50)^2)/49)
```
H0:KNN from scratch has lower mean accuracy compared to sklearn counterpart
H1:KNN from scratch has greater mean accuracy compared to sklearn counterpart
```{r}
t.test(data_scratch$Accuracy, data_sklearn$Accuracy, alternative = "greater", paired = T)
```

```{r}
#c(qt(0.025, nu),qt(0.975, nu))
c(qt(0.05, nu),qt(0.95, nu))
```
Variance Test for Precision Metric

```{r}
var.test(data_scratch$Precision, data_sklearn$Precision, alternative = "two.sided")
```

```{r}
c(qf(0.025, 49, 49), qf(0.975, 49, 49))
```
```{r}
a <- var(data_scratch$Precision)
b <- var(data_sklearn$Precision)

nu <- (((a/50) + (b/50)) ^ 2) / (((a/50)^2)/49) + (((b/50)^2)/49)
```

H0:KNN from scratch has lower mean precision compared to sklearn counterpart
H1:KNN from scratch has greater mean precision compared to sklearn counterpart
```{r}
t.test(data_scratch$Precision, data_sklearn$Precision, alternative = "greater", paired = T)
```
```{r}
c(qt(0.05, nu),qt(0.95, nu))
```


Variance Test for Recall Metric

```{r}
var.test(data_scratch$Recall, data_sklearn$Recall, alternative = "two.sided")
```

```{r}
c(qf(0.025, 49, 49), qf(0.975, 49, 49))
```
```{r}
a <- var(data_scratch$Recall)
b <- var(data_sklearn$Recall)

nu <- (((a/50) + (b/50)) ^ 2) / (((a/50)^2)/49) + (((b/50)^2)/49)
```

H0:KNN from scratch has lower mean recall compared to sklearn counterpart
H1:KNN from scratch has greater mean recall compared to sklearn counterpart
```{r}
t.test(data_scratch$Recall, data_sklearn$Recall, alternative = "greater", paired = T)
```
```{r}
c(qt(0.05, nu),qt(0.95, nu))
```


Variance Test for F1 Score Metric

```{r}
var.test(data_scratch$F1.Score, data_sklearn$F1.Score, alternative = "two.sided")
```

```{r}
c(qf(0.025, 49, 49), qf(0.975, 49, 49))
```
```{r}
a <- var(data_scratch$F1.Score)
b <- var(data_sklearn$F1.Score)

nu <- (((a/50) + (b/50)) ^ 2) / (((a/50)^2)/49) + (((b/50)^2)/49)
```

H0:KNN from scratch has lower mean f1 score compared to sklearn counterpart
H1:KNN from scratch has greater mean f1 score compared to sklearn counterpart
```{r}
t.test(data_scratch$F1.Score, data_sklearn$F1.Score, alternative = "greater", paired = T)
```
```{r}
c(qt(0.05, nu),qt(0.95, nu))

```

Variance Test for Sensitivity Metric

```{r}
var.test(data_scratch$Sensitivity, data_sklearn$Sensitivity, alternative = "two.sided")
```

```{r}
c(qf(0.025, 49, 49), qf(0.975, 49, 49))
```
```{r}
a <- var(data_scratch$Sensitivity)
b <- var(data_sklearn$Sensitivity)

nu <- (((a/50) + (b/50)) ^ 2) / (((a/50)^2)/49) + (((b/50)^2)/49)
```

H0:KNN from scratch has lower mean f1 score compared to sklearn counterpart
H1:KNN from scratch has greater mean f1 score compared to sklearn counterpart
```{r}
t.test(data_scratch$Sensitivity, data_sklearn$Sensitivity, alternative = "greater", paired = T)
```
```{r}
c(qt(0.05, nu),qt(0.95, nu))

```


Variance Test for Specificity Metric

```{r}
var.test(data_scratch$Specificity, data_sklearn$Specificity, alternative = "two.sided")
```

```{r}
c(qf(0.025, 49, 49), qf(0.975, 49, 49))
```
```{r}
a <- var(data_scratch$Specificity)
b <- var(data_sklearn$Specificity)

nu <- (((a/50) + (b/50)) ^ 2) / (((a/50)^2)/49) + (((b/50)^2)/49)
```

H0:KNN from scratch has greater mean specificity compared to sklearn counterpart
H1:KNN from scratch has lower mean specificity compared to sklearn counterpart
```{r}
t.test(data_scratch$F1.Score, data_sklearn$F1.Score, alternative = "greater", paired = T)
```
```{r}
c(qt(0.05, nu),qt(0.95, nu))

```


Variance Test for Processing Time Metric

```{r}
var.test(data_scratch$Processing.Time, data_sklearn$Processing.Time, alternative = "two.sided")
```

```{r}
c(qf(0.025, 49, 49), qf(0.975, 49, 49))
```
```{r}
a <- var(data_scratch$Processing.Time)
b <- var(data_sklearn$Processing.Time)

nu <- (((a/50) + (b/50)) ^ 2) / (((a/50)^2)/49) + (((b/50)^2)/49)
```

H0:KNN from scratch has lower mean f1 score compared to sklearn counterpart
H1:KNN from scratch has greater mean f1 score compared to sklearn counterpart
```{r}
t.test(data_scratch$Processing.Time, data_sklearn$Processing.Time, alternative = "greater", paired = T)
```
```{r}
c(qt(0.05, nu),qt(0.95, nu))

```
```{r}

```



